Towards a computational framework using finite element methods with Arbitrary Lagrangian-Eulerian approach for swimmers with contact

### 2024-08-13 article.swimmer-framework-contact.springer.tex
add git info
fix compilation
add xspace package + ignore
#1
rename according to workflow
add latex workflow #1

\usepackage{newtxtext}       % 
\usepackage[varvw]{newtxmath}       % selects Times Roman as basic font
\usepackage{siunitx}
\usepackage{tikz}
% \usepackage[authoryear,sort]{natbib}
% \usepackage[natbib=true]{biblatex}

@@

% see the list of further useful packages
\newcommand{\feelpp}{\texttt{Feel++}}
\newcommand{\Fluid}{\mathcal{F}} % fluid domain
\newcommand{\Real}{\mathbb{R}} % real number space
\newcommand{\Alemap}{\mathcal{A}} % Ale map
\newcommand{\ALE}{ALE} % ALE acronym
\newcommand{\Vel}{u} % fluid velocity
\newcommand{\Pres}{p} % fluid pressure
\newcommand{\Density}{\rho} % density
\newcommand{\Viscosity}{\mu} % fluid viscosity
\newcommand{\tvel}{U} % rigid body linear velocity
\newcommand{\angvel}{\omega} % rigid body angular velocity
\newcommand{\Rmat}{R} % rotation matrix frame
\newcommand{\Angle}{\theta}
\newcommand{\Inertia}{I} % inertia tensor/moment for rigid body
\newcommand{\mass}{m} % mass of the rigid body
\newcommand{\CenterMass}{x^{CM}} % center of mass of the rigid body
\newcommand{\CenterMassi}{x_{CM}^i}
\newcommand{\Solid}{\mathcal{S}} % region occupied by the body
\newcommand{\normal}{n} % outer normal to the fluid domain
\newcommand{\CompDomain}{\Fluid}
\newcommand{\dx}{\, \mathrm{d}x}
\newcommand{\Id}{\mathbb{I}}
\newcommand{\Disp}{\eta}
\newcommand{\dX}{\,\mathrm{d}X}
\newcommand{\cpp}{\texttt{C++}}
\newcommand{\R}{\mathbb{R}}
% DOUBLEHAT
\newlength{\dhatheight}
\newcommand{\hhatDS}[1]{%
	\settoheight{\dhatheight}{\ensuremath{\hat{#1}}}%
	\addtolength{\dhatheight}{-0.35ex}%
	\hat{\vphantom{\rule{1pt}{\dhatheight}}%
		\smash{\hat{#1}}}}
\newcommand{\hhatTS}[1]{%
	\settoheight{\dhatheight}{\ensuremath{\hat{#1}}}%
	\addtolength{\dhatheight}{-0.35ex}%
	\hat{\vphantom{\rule{1pt}{\dhatheight}}%
		\smash{\hat{#1}}}}    
\newcommand{\hhatS}[1]{%
	\settoheight{\dhatheight}{\ensuremath{\scriptstyle{\hat{#1}}}}%
	\addtolength{\dhatheight}{-0.175ex}%
	\hat{\vphantom{\rule{1pt}{\dhatheight}}%
		\smash{\hat{#1}}}}
\newcommand{\hhatSS}[1]{%
	\settoheight{\dhatheight}{\ensuremath{\scriptscriptstyle{\hat{#1}}}}%
	\addtolength{\dhatheight}{-0.07ex}%
	\hat{\vphantom{\rule{1pt}{\dhatheight}}%
		\smash{\hat{#1}}}}
\newcommand{\doublehat}[1]{\hat{#1}}%{\mathchoice{\hhatDS{#1}}{\hhatTS{#1}}{\hhatS{#1}}{\hhatSS{#1}}}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\linewidth]{Figures/3d_sperm_planar/3dswimmer_00.png}
	\includegraphics[width=0.45\linewidth]{Figures/3d_sperm_planar/3dswimmer_0dot5.png}
	\includegraphics[width=0.45\linewidth]{Figures/3d_sperm_planar/3dswimmer_1dot85.png}
	\includegraphics[width=0.45\linewidth]{Figures/3d_sperm_planar/3dswimmer_2dot65.png}
	\caption{Three dimensional simulation of a swimming sperm cell propagating planar waves on its flagellum. Flagellar beating is restricted to $xy$ plane, and the maximal amplitude of the wave is $A_{max}=\SI{4}{\micro\meter}$. The four images show the position and shape of the sperm cell at the time instants $t=\SI{0}{\second}$, $t=\SI{0.5}{\second}$, $t=\SI{1.85}{\second}$ and $t=\SI{2.65}{\second}$. }
	\label{Fig:3dsperm_planar}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.55]{Figures/three-sphere/3ss.png}

@@

\begin{figure}[h!]
    \centering
    \centerline{\includegraphics[scale=0.5]{Figures/three-sphere/sw_motion2_tmp.png}}
    \caption{Behavior of a three-sphere swimmer swimming towards the boundary of 
	the computational domain. The swimmer reorients due to contact forces and hydrodynamic interactions with the plane wall.}
    \label{fig:3ss}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.175]{Figures/three-sphere/Horizontal.png}
    \includegraphics[scale=0.175]{Figures/three-sphere/vertical.png}
    \caption{Examples of vertical and horizontal displacements of three-sphere swimmers. The orange continuous lines corresponds to the $x$ and $y$ trajectories of a swimmer heading towards the boundary of the domain and reorienting after the contact with the wall. The blue dotted line describe the trajectories of a swimmer swimming far from the wall and parallel to it.}
    \label{fig:3ss_2}
\end{figure}

@@

        \includegraphics[scale=0.2]{Figures/squirmer/squirmers.png}

	\includegraphics[scale=0.14]{Figures/squirmer/t=0.1.png}
	\includegraphics[scale=0.14]{Figures/squirmer/t=2.5.png}
	\includegraphics[scale=0.14]{Figures/squirmer/t=3.5.png}
	\includegraphics[scale=0.14]{Figures/squirmer/t=8_.png}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.85\linewidth]{Figures/zf/zf.png}

>>>>

\usepackage{newtxtext}       % 
\usepackage[varvw]{newtxmath}       % selects Times Roman as basic font
\usepackage{siunitx}
\usepackage{tikz}
% \usepackage[authoryear,sort]{natbib}
% \usepackage[natbib=true]{biblatex}
\usepackage[colorlinks,citecolor=blue]{hyperref}
\IfFileExists{.git/gitHeadInfo.gin}{
    \usepackage[pcount,grumpy,mark,markifdirty]{gitinfo2}
}{%
    \usepackage[local,pcount,grumpy,mark,markifdirty]{gitinfo2}
}

% Feel++ macro 
\usepackage{xspace}
\newcommand{\feelpp}{Feel\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}\xspace}

@@

% see the list of further useful packages
\newcommand{\Fluid}{\mathcal{F}} % fluid domain
\newcommand{\Real}{\mathbb{R}} % real number space
\newcommand{\Alemap}{\mathcal{A}} % Ale map
\newcommand{\ALE}{ALE} % ALE acronym
\newcommand{\Vel}{u} % fluid velocity
\newcommand{\Pres}{p} % fluid pressure
\newcommand{\Density}{\rho} % density
\newcommand{\Viscosity}{\mu} % fluid viscosity
\newcommand{\tvel}{U} % rigid body linear velocity
\newcommand{\angvel}{\omega} % rigid body angular velocity
\newcommand{\Rmat}{R} % rotation matrix frame
\newcommand{\Angle}{\theta}
\newcommand{\Inertia}{I} % inertia tensor/moment for rigid body
\newcommand{\mass}{m} % mass of the rigid body
\newcommand{\CenterMass}{x^{CM}} % center of mass of the rigid body
\newcommand{\CenterMassi}{x_{CM}^i}
\newcommand{\Solid}{\mathcal{S}} % region occupied by the body
\newcommand{\normal}{n} % outer normal to the fluid domain
\newcommand{\CompDomain}{\Fluid}
\newcommand{\dx}{\, \mathrm{d}x}
\newcommand{\Id}{\mathbb{I}}
\newcommand{\Disp}{\eta}
\newcommand{\dX}{\,\mathrm{d}X}
\newcommand{\cpp}{\texttt{C++}}
\newcommand{\R}{\mathbb{R}}
% DOUBLEHAT
\newlength{\dhatheight}
\newcommand{\hhatDS}[1]{%
	\settoheight{\dhatheight}{\ensuremath{\hat{#1}}}%
	\addtolength{\dhatheight}{-0.35ex}%
	\hat{\vphantom{\rule{1pt}{\dhatheight}}%
		\smash{\hat{#1}}}}
\newcommand{\hhatTS}[1]{%
	\settoheight{\dhatheight}{\ensuremath{\hat{#1}}}%
	\addtolength{\dhatheight}{-0.35ex}%
	\hat{\vphantom{\rule{1pt}{\dhatheight}}%
		\smash{\hat{#1}}}}    
\newcommand{\hhatS}[1]{%
	\settoheight{\dhatheight}{\ensuremath{\scriptstyle{\hat{#1}}}}%
	\addtolength{\dhatheight}{-0.175ex}%
	\hat{\vphantom{\rule{1pt}{\dhatheight}}%
		\smash{\hat{#1}}}}
\newcommand{\hhatSS}[1]{%
	\settoheight{\dhatheight}{\ensuremath{\scriptscriptstyle{\hat{#1}}}}%
	\addtolength{\dhatheight}{-0.07ex}%
	\hat{\vphantom{\rule{1pt}{\dhatheight}}%
		\smash{\hat{#1}}}}
\newcommand{\doublehat}[1]{\hat{#1}}%{\mathchoice{\hhatDS{#1}}{\hhatTS{#1}}{\hhatS{#1}}{\hhatSS{#1}}}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\linewidth]{img-3d_sperm_planar-3dswimmer_00.png}
	\includegraphics[width=0.45\linewidth]{img-3d_sperm_planar-3dswimmer_0dot5.png}
	\includegraphics[width=0.45\linewidth]{img-3d_sperm_planar-3dswimmer_1dot85.png}
	\includegraphics[width=0.45\linewidth]{img-3d_sperm_planar-3dswimmer_2dot65.png}
	\caption{Three dimensional simulation of a swimming sperm cell propagating planar waves on its flagellum. Flagellar beating is restricted to $xy$ plane, and the maximal amplitude of the wave is $A_{max}=\SI{4}{\micro\meter}$. The four images show the position and shape of the sperm cell at the time instants $t=\SI{0}{\second}$, $t=\SI{0.5}{\second}$, $t=\SI{1.85}{\second}$ and $t=\SI{2.65}{\second}$. }
	\label{Fig:3dsperm_planar}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.55]{img-three-sphere-3ss.png}

@@

\begin{figure}[h!]
    \centering
    \centerline{\includegraphics[scale=0.5]{img-three-sphere-sw_motion2_tmp.png}}
    \caption{Behavior of a three-sphere swimmer swimming towards the boundary of 
	the computational domain. The swimmer reorients due to contact forces and hydrodynamic interactions with the plane wall.}
    \label{fig:3ss}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.175]{img-three-sphere-Horizontal.png}
    \includegraphics[scale=0.175]{img-three-sphere-vertical.png}
    \caption{Examples of vertical and horizontal displacements of three-sphere swimmers. The orange continuous lines corresponds to the $x$ and $y$ trajectories of a swimmer heading towards the boundary of the domain and reorienting after the contact with the wall. The blue dotted line describe the trajectories of a swimmer swimming far from the wall and parallel to it.}
    \label{fig:3ss_2}
\end{figure}

@@

        \includegraphics[scale=0.2]{img-squirmer-squirmers.png}

	\includegraphics[scale=0.14]{img-squirmer-t=0.1.png}
	\includegraphics[scale=0.14]{img-squirmer-t=2.5.png}
	\includegraphics[scale=0.14]{img-squirmer-t=3.5.png}
	\includegraphics[scale=0.14]{img-squirmer-t=8_.png}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.85\linewidth]{img-zf-zf.png}
